---
title: "Robust statistic tutorial 1"
author: "XIXI"
date: "2025-03-19"
output: html_document
---
#1. The dataset comprises 26 measurements of hardness, often used to illustrate robust statistical methods.
#570, 565, 575, 580, 590, 600, 610, 620, 625, 630, 635, 640, 645, 650,
#660, 665, 670, 675, 680, 690, 700, 710, 720, 730, 740, 750

#(a) Compute descriptive statistics for this dataset: mean, median, standard deviation, fourth spread and MAD.

```{r}
data_1 <- c(570, 565, 575, 580, 590, 600, 610, 620, 625, 630, 635, 640, 645, 650,660, 665, 670, 675, 680, 690, 700, 710, 720, 730, 740, 750)
#这几个descriptive statistics有什么不同？分别用在哪些场所 
a_mean <- mean(data_1)
a_median <- median(data_1)
a_sd <- sd(data_1)
a_iqr <- IQR(data_1)
a_mad <- mad(data_1)
a_mean
a_median
a_sd
a_iqr
a_mad
```
#(b) Compute the standard and robust confidence intervals for this dataset.(计算数据的标准和稳健置信区间)
```{r}
#标准置信区间
t.test(data_1)$conf.int
#稳健置信区间


```

#(c) Using visual representation, depict the distribution of hardness measurements and highlight the presence of outliers.
```{r}

  boxplot(data_1, col = "lightgray", main = "Boxplot of Hardness Measurements",
        ylab = "Hardness", horizontal = FALSE)
x <- boxplot.stats(data_1)$out
#结果是“numeric(0)”表示没有异常值

#做密度图
library(ggplot2)

# 创建数据框
df <- data.frame(data_1)
# 绘制直方图加密度图
ggplot(df, aes(x = data_1)) +
  geom_histogram(aes(y = ..density..), bins = 10, fill = "lightblue", color = "black", alpha = 0.7) +  # 直方图
  geom_density(color = "red", lwd = 1.2) +  # 密度曲线
  labs(title = "Histogram & Density Plot of Hardness Measurements",
       x = "Hardness", y = "Density") +
  theme_minimal()



```

#(d) Comment on your findings.

#2. The following data were generated from a Uniform distribution, U(0,1):
#0.10 0.15 0.20 0.35 0.45 0.55 0.65 0.75 0.85 0.95
#Calculate the following
#• Sample mean
#• Sample median
#• 10% trimmed mean
```{r}
d_2<- c(0.10,0.15,0.20, 0.35, 0.45, 0.55 ,0.65 ,0.75 ,0.85, 0.95)
mean_2 <- mean(d_2)
med_2 <- median(d_2)
trim_2 <- mean(d_2,trim=0.1)
mean_2
med_2
trim_2
```
## 0.5,0.5,0.49

#Now, replace the largest value from the dataset with 5.0:
#Recalculate the new sample mean, median and the 10% trimmed mean.
#Interpret your findings.
```{r}
d_3<- c(0.10,0.15,0.20, 0.35, 0.45, 0.55 ,0.65 ,0.75 ,0.85, 5)
mean_3 <- mean(d_3)
med_3 <- median(d_3)
trim_3 <- mean(d_3,trim=0.1)
mean_3
med_3
trim_3
```

#0.905,0.5,0.49375
##发现：我发现一组数据（0.10,0.15,0.20, 0.35, 0.45, 0.55 ,0.65 ,0.75 ,0.85, 0.95）求这三个值时，均值，中位数，截尾均值三个数值是差不多的都在0.5左右，因为这组数据比较平均，没有异常值。然后把这组数据的最大值改为5，均值mean升高到0.95，中位数还是0.5，截尾均值也没有变化，一样是0.49375，说明中位数和截尾均值比较稳健，不受outlier值影响，但是mean只适合平稳的一组数值，受异常值影响大


